Adaptive Resolution Simulation in Equilibrium and Beyond

### 2014-11-10 writeDown/pub.epj/paper.tex
add the velocity auto-correlation

%
\begin{document}
%
\title{Adaptive Resolution Simulation: Theoretical Fundations and Open Questions}
\author{Han Wang\inst{1}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{2}}
%
\institute{Zuse Institut Berlin, \and Institut f\"ur Mathematik, Freie Universit\"at Berlin}
%
\abstract{
Insert your abstract here.
} %end of abstract
%
\maketitle
%

@@

Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular system.
The terminology ``concurrent multiscale simulation'' means that
part of the system is simulated with higher resolution molecular models for the
purpose of accuracy, and \emph{in the meanwhile} the rest of the system is
simulated with lower resolution models for the purpose of saving computational cost.
The AdResS is, therefore, suitable for the systems that different physcial
phenomena happen concurrently at different time and length scales. For example,
the structure of a protein and its solvation shell
should be resolved at the atomistic level, while far away form the protein,
the only the hydrodynamic properties are of interest, which can be studied with satisfactory
accuracy with very coarse-grained or even continum
models~\cite{zavadlav2014adaptive,zavadlav2014adaptive1,delgado2009coupling}.
Similar  
techniques sharing the ``concurrent'' idea of multiscale simulation can be found in, for example, Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.

@@

\section{The hybrid region: bridging the molecular models of different resolutions}
\label{sec:design}
The AdResS uses a weighting function $w(\vect r)$ that is a scalor
function defined over the simulation region to denote the resolution
of the system. In the atomistic region the value of the
weighting function is usually set to 1, while in the coarse-grained
region it is usually set to 0. In between, there is a bybrid region
that is denoted by $\Omega_\HY$
(or called transition region), where the molecules
has both the atomistic and coarse-grained resolutions, and the weighting function
goes smoothly from 1 to 0. The way of designing the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region is
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
Since all interactions (including the electrostatic interction) are treated
by cut-off method, the weighting function requires the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$). 
The benefite of this setting is that the atomistic
region is not directly interacting with the coarse-grained region,
so there is no extra work for modeling the interactions between the atomistic
and coarse-grained resolutions.

Both the atomistic and coarse-grained intermolecular interactions are
well defined in the atomistic region and coarse-grained regions,
respectively.  To setup an AdResS simulation, one needs to define the
interactions in the hybrid region. There are in general two
possibilities: force interpolation and the potential interpolation.
The force interpolation approach defines the hybrid force between two
molecules (saying $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
\begin{align}\label{eqn:f-f-interpol}
  {\vect F}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
where $w_\moleidxone = w(\vect r_\moleidxone)$ is the weighting function
measured at the center-of-mass (COM) position of molecule $\moleidxone$.
It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
exist a potential so that the force interpolation is derived by taking the negative gradient of the potential,
unless the coarse-grained interaction is identical to the atomistic interaction~\cite{praprotnik2011comment,dellesite2007some}.
It is easy to show that the force interpolation satisfies the momentum conservation: Since
both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$, from the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.

The potential interpolation approach defines the hybrid energy by the same idea:
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscipt ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
This force is defined as the force of changing representation:
It should be noted that
the last term breaks the Newton's third law, therefore the force of potential interpolation
does not conserves the momentum.
We define the accumulative effect of this term by the force of changing representation:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

\begin{table}
  \centering
  \caption{A summary of the fundamental conservation laws in mechanics 
    satisfied by the normal molecular system and AdResS systems defined by force and potential interpolations.}
  \label{tab:conv-laws}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}lcc}\hline\hline
    &         Momentum Consv.     &       Energy Consv. \\
    Normal molecular System     &       {Yes}        &       {Yes}\\      
    AdResS force interpol.   &       {Yes}        &       {No}\\      
    AdResS potential interpol.  &     {No}  &       {Yes}\\\hline\hline
  \end{tabular*}
\end{table}
The fundamental conservation laws satisfied by both the force and potential interpolations
are summarized in Tab.~\ref{tab:conv-laws}. Unlike normal molecular systems, in which both
the momentum and energy are conserved, neither of the AdResS systems conserves
both laws. The breaks of these mechanics conservations have substantial influence on the thermodynamic
properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}). The choice of the interpolation scheme depends on
the practical requirement, for example, in some systems it is crucial to have the momentum
conservation, then the force interpolation is prefered, and vice versa.
In equilibrium case, we will show later in Sec.~\ref{sec:statistical}
that both approaches approximately sample the grand-canonial ensemble.

When the intermolecular force is defined by either
Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
force exserts on one molecule is given by the normal adding up rule:
\begin{align}
  \vect F_\moleidxone = \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}, \quad \vect F^V_\moleidxone = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo}
\end{align}
On the force on the atomistic DOFs of a hybrid molecules is distributed 
by, taking atom $\atomidxone$ on molecule $\moleidxone$ for example,
\begin{align}
  \vect F_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F_\moleidxone, \quad   \vect F^V_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F^V_\moleidxone 
\end{align}
where $m_\atomidxone$ is the mass of atom, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.

Before discussing the statistical and thermodynamic properties of AdResS, a few comments on the
choice of the weighting function should be added. 
In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighing function that
introduce a buffer region so that the molecules with the atomistic resolution
interacts with the hybrid region via the atomistic intermolecular interaction:
\begin{equation}\label{eqn:new-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &1 && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c \\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT) - r_c}{d_{{\HY}} - r_c}\,\Big] && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) \geq r_c\\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
The minimum thickness of the hybrid region is therefore $2r_c$.
It worth noting that the coarse-grained region does not requires a buffer in the hybrid region, because
by definition the coarse-grained region interacts with the hybrid region via the coarse-grained intermolecular interaction.
The new definition~\eqref{eqn:new-w} is crucial for the equilibrium statistical properties of the AdResS,
however, the extra cost of is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
which is treated in atomistic resolution. This cost is relatively small for systems with large atomistic region.

\recheck{Remark, add the remark of inversed weighting function}

@@

To consider the accuracy of the AdResS simulation, we always compare it with a
atomistic reference system, which is of the same size as the AdResS system, and contains the same number of molecules.
If the statistal properties of the atomistic region in the AdResS simulation
is same as the corresponding subregion in the atomistic reference, then
the atomistic region is embeded into the AdResS system as if it were embeded in to
an atomistic environment, and the AdResS simulation is of good accuracy.
\recheck{comments on the ``atomistic region'' of the reference system}

We denote the number of molecules, volume and temperture of the system by $N$, $V$ and $T$, respectively.
The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
the desired equilibrium.
% The word ``desired'' means that
% the atomistic region of the AdResS system should reproduce the equilibrium properties corresponding subregion of the reference
% system.
The thermodynamic variables for subregions are specified by the subscript,
for example, the those of the atomistic region are 
$N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
are denoted by adding ``$\HY$'' and ``$\CG$'', respectively.
Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
in the AdResS system.
In equilibrium, the temperature is uniform across the system: $T = T_\AT = T_\HY = T_\CG$.
This is achieved in practice by coupling the whole system to a Langevin thermostat.
The pressure and chemical potential of the atomistic and coarse-grained regions
are denoted by $\{p_\AT, \mu_\AT\}$
and $\{p_\CG, \mu_\CG\}$, respectively.
The DOFs of molecules indexed $\moleidxone$ are $\vect x_\moleidxone = \{\vect r_\moleidxone, \vect p_\moleidxone\}$, where
$\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
All DOFs of the system is denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
generality, the first molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ in hybrid region, and
the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
\redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/system.thermo/system.eps}
  \caption{A schematic plot of the AdResS system in thermodynamic
    equilibrium. The number of molecules, volume and temperature of
    the atomistic and coarse-grained regions are denoted by $\{N_\AT,
    V_\AT, T\}$ and $\{N_\AT, V_\AT, T\}$, respectively. The filter
    allows free exchange of molecules between atomistic and
    coarse-grained regions.}
  \label{fig:system-thermo}
\end{figure}

We consider the system in the thermodynamic limit: both the atomistic
and the coarse-grained regions are infinitely large, and at the same
time, the atomistic region is much larger than the coarse-grained
region. The hybrid region is much smaller than both the atomistic and
coarse-grained regions.  Therefore, the number of molecules in the
three regions satisfies $N_\CG\gg N_\AT\gg N_\HY$.  The coarse-grained
region can be treated as an infinitely large particle and energy
reservior of the atomistic region, and the hybrid region is an
infinitely thin filter that changes molecular resolution when a
molecule passes by (see Fig.~\ref{fig:system-thermo}). In the
thermodynamic limit, if there were no change of resolution (or
considering the full atomistic reference system), it is obvious that
the subregion corresponds to the atomistic region samples the
grand-canonial ensemble.  The question regarding the accuracy of
AdResS can be asked by: How accurately the atomistic region samples
the grand-canonial ensemble in the thermodynamic limit. Being more
specifically, we want to prove the probability density of the atomistic region satisfies
\begin{align}\label{eqn:dist-0}
  p(\vect x_\AT, N_\AT) \approx \frac{1}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT - \beta \mh^\AT(\vect x_\AT)} \Big\}
\end{align}
where $\mu^\ast_\AT$ is the chemical potential of reference system in
desired equilibrium, $\mathcal Z$ is the partition function
normalizing the probability density, and $\mh^\AT$ is the atomistic
Hamiltonian defined in the the subregion of the reference system that
corresponds to the atomistic region of the AdResS system.

@@

In the reference system, if the equilibrium state is achieved, then
the temperature, pressure and chemical potential of the atomistic and
coarse-grained subregions match. In AdResS system, the global uniform
temperture distrubution in equilibrium is impoosed by the Langevin
thermostat.  However, extra term appear in the pressure or chemical
potential relation when the momentum or energy conservation is absent
(see Tab.~\ref{tab:conv-laws}), respectively.

>>>>

%
\begin{document}
%
\title{Adaptive Resolution Simulation in Equilibrium and Beyond}
\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{3}}
%
\institute{CAEP Software Center for High Performance Numerical Simulation, Beijing, China
  \and Zuse Institute Berlin (ZIB), Germany
  \and Institut f\"ur Mathematik, Freie Universit\"at Berlin, Berlin, Germany}
%
\abstract{
Insert your abstract here.
} %end of abstract
%
\maketitle
%

@@

Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poma2010classical,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular system.
The terminology ``concurrent multiscale simulation'' means that
part of the system is simulated with higher resolution molecular models for the
purpose of accuracy, and \emph{in the meanwhile} the rest of the system is
simulated with lower resolution models for the purpose of saving computational cost.
The AdResS is, therefore, suitable for the systems that different physcial
phenomena happen concurrently at different time and length scales. For example,
the structure of a protein and its solvation shell
should be resolved at the atomistic level, while far away form the protein,
the only the hydrodynamic properties are of interest, which can be studied with satisfactory
accuracy with very coarse-grained or even continum
models~\cite{zavadlav2014adaptive,zavadlav2014adaptive1,delgado2009coupling}.
Similar  
techniques sharing the ``concurrent'' idea of multiscale simulation can be found in, for example, Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.

@@

\section{The hybrid region: bridging the molecular models of different resolutions}
\label{sec:design}

In most cases discussed in this work, we refer to higher resolution as the classical atomistic model, while
the lower resolution as the coarse-grained molecular model. However,
one should keep in mind that the ``atomistic'' and ``coarse-grained'' resolutions
may refer to more general molecular models, e.g.~the higher resolution can be
path-integral representation~\cite{poma2010classical}, and lower resolution can be continuous
hydrodynamic description~\cite{delgado2009coupling}.

In AdResS scheme, the simulation region $\Omega$ is 
is decomposed without overlapping into 3 regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
The AdResS uses a scalor weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region is
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
Since all interactions (including the electrostatic interction) in AdResS are treated
by cut-off method, the weighting function requires the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$). 
The benefite of this setting is that the atomistic
region is not directly interacting with the coarse-grained region,
so there is no extra work for modeling the cross-scale interactions.

The intermolecular interactions are
well defined in the atomistic and coarse-grained regions by the corresponding models.
To setup an AdResS simulation, one only needs to define the
interactions in the hybrid region. There are in general two
possibilities: force interpolation and the potential interpolation.
The force interpolation approach defines the hybrid force between two
molecules (indexed by $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
\begin{align}\label{eqn:f-f-interpol}
  {\vect F}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
where $w_\moleidxone = w(\vect r_\moleidxone)$ is the weighting function
measured at the center-of-mass (COM) position of molecule $\moleidxone$.
It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
exist a potential so that the force interpolation is derived by taking the negative gradient of the potential,
unless the coarse-grained interaction is identical to the atomistic interaction~\cite{praprotnik2011comment,dellesite2007some}.
It is easy to show that the force interpolation satisfies the momentum conservation: Since
both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$. From the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.

The potential interpolation approach defines the hybrid energy by
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscipt ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
This force is defined as the force of changing representation:
It should be noted that
the last term breaks the Newton's third law, therefore the force of potential interpolation
does not conserve the momentum.
We define the accumulative effect of this term by the force of changing representation:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

\begin{table}
  \centering
  \caption{A summary of the fundamental conservation laws in mechanics 
    satisfied by the normal molecular system and AdResS systems defined by force and potential interpolations.}
  \label{tab:conv-laws}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}lcc}\hline\hline
    &         Momentum Consv.     &       Energy Consv. \\
    Normal molecular System     &       {Yes}        &       {Yes}\\      
    AdResS force interpol.   &       {Yes}        &       {No}\\      
    AdResS potential interpol.  &     {No}  &       {Yes}\\\hline\hline
  \end{tabular*}
\end{table}
The fundamental conservation laws satisfied by both the force and potential interpolations
are summarized in Tab.~\ref{tab:conv-laws}. Unlike normal molecular systems, in which both
the momentum and energy are conserved, neither of the AdResS systems conserves
both laws. The breaks of these mechanics conservations have substantial influence on the thermodynamic
properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}). The choice of the interpolation scheme depends on
the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
conservation, then the force interpolation is prefered.
In equilibrium case, we will show later in Sec.~\ref{sec:statistical}
that both approaches approximately sample the grand-canonial ensemble.

When the intermolecular force is defined by either
Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
force exserts on one molecule is given by the normal adding up rule:
\begin{align}
  \vect F_\moleidxone = \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}, \quad \vect F^V_\moleidxone = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo}
\end{align}
The force on the atomistic DOFs of a hybrid molecules is distributed 
by, 
\begin{align}
  \vect F_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F_\moleidxone, \quad   \vect F^V_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F^V_\moleidxone 
\end{align}
where  $\atomidxone$ is the indexes of atoms in molecule $\moleidxone$.
$m_\atomidxone$ is the mass of atom, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.

Before discussing the statistical and thermodynamic properties of AdResS, a remark on the
choice of the weighting function should be added. 
In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighing function with
a buffer region so that the atomistic region
interacts with the hybrid region via the atomistic intermolecular interaction:
\begin{equation}\label{eqn:new-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &1 && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c \\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT) - r_c}{d_{{\HY}} - r_c}\,\Big] && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) \geq r_c\\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
The minimum thickness of the hybrid region is therefore $2r_c$.
It worth noting that the coarse-grained region does not requires a buffer in the hybrid region, because
by definition the coarse-grained region interacts with the hybrid region via the coarse-grained intermolecular interaction.
The new definition~\eqref{eqn:new-w} is crucial for the equilibrium statistical properties of the AdResS,
however, the extra cost of is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
which is treated in atomistic resolution. This cost is relatively small for systems with large atomistic region.

% \recheck{Remark, add the remark of inversed weighting function}
% \vskip .2cm
% \noindent\textbf{Remark}: In the case where the high-resolution simulation
% is extremely expensive, e.g.~the path-integral AdResS~\cite{poma2010classical},
% the extra cost for simulating with buffer region is therefore not desirable.
% One possible solution is to assign the value of weighting function in an reversed way:
% it taks 0 in high-resolution region, while takes 1 in low-resolution region.
% With the reversed weighting, the buffer region is on the coarse-grained side,

@@

In order to consider the accuracy of the AdResS from statistical point of view, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in the AdResS 
is same as the corresponding subregion in the atomistic reference, then
the AdResS  is of good accuracy (see the comparision indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximate the thermodynamic limit, the subsystem is
subject to the grand-canonial ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS is also subject to the grand-canonial ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

% the atomistic region is embeded into the AdResS system as if it were embeded in to an atomistic environment,
% and the AdResS  is of good accuracy (see the red arrow in Fig.~\ref{fig:compare}).
% Here the corresponding atomistic region in the reference sys
% \recheck{comments on the ``atomistic region'' of the reference system}
\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/system.water/compare.eps}
  \caption{A schematic plot of the comparision between the AdResS system (left) and the full atomistic reference system (right).}
  \label{fig:compare}
\end{figure}

We denote the number of molecules, volume and temperture of the system by $N$, $V$ and $T$, respectively.
The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
the \emph{desired equilibrium} of AdResS.
% The word ``desired'' means that
% the atomistic region of the AdResS system should reproduce the equilibrium properties corresponding subregion of the reference
% system.
The thermodynamic variables of the subregions are specified by the subscript,
for example, the those of the atomistic region are 
$N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
are denoted by adding ``$\HY$'' and ``$\CG$'', respectively.
Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
in the AdResS system.
In equilibrium, the temperature is uniform across the system: $T = T_\AT = T_\HY = T_\CG$.
This is achieved in practice by coupling the whole system to a Langevin thermostat.
The pressure and chemical potential of the atomistic and coarse-grained regions
are denoted by $\{p_\AT, \mu_\AT\}$
and $\{p_\CG, \mu_\CG\}$, respectively.
The DOFs of molecules indexed $\moleidxone$ are $\vect x_\moleidxone = \{\vect r_\moleidxone, \vect p_\moleidxone\}$, where
$\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
All DOFs of the system is denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
generality, the first molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ in hybrid region, and
the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
It should be noted that for simplicity, we do not explicitly consider the number of DOFs are different for an atomistic
and a coarse-grained molecule, and uniformly encode them by the vector $\vect x$.
% so it is acutally 
% \redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.3\textwidth]{figs/system.thermo/system.eps}
%   \caption{A schematic plot of the AdResS system in thermodynamic
%     equilibrium. The number of molecules, volume and temperature of
%     the atomistic and coarse-grained regions are denoted by $\{N_\AT,
%     V_\AT, T\}$ and $\{N_\AT, V_\AT, T\}$, respectively. The filter
%     allows free exchange of molecules between atomistic and
%     coarse-grained regions.}
%   \label{fig:system-thermo}
% \end{figure}

The thermodynamic limit is taken in the sense that both the atomistic
and the coarse-grained regions are infinitely large, and at the same
time, the atomistic region is much larger than the coarse-grained
region. The hybrid region is much smaller than both the atomistic and
coarse-grained regions.  Therefore, the volumes of the
three regions satisfies $V_\CG\gg V_\AT\gg V_\HY$.  The coarse-grained
region can be treated as an infinitely large particle and energy
reservior of the atomistic region, and the hybrid region is an
infinitely thin filter that changes molecular resolution when a
molecule passes by. In the
thermodynamic limit, if there were no change of resolution (or
considering the full atomistic reference system), it is obvious that
the subregion corresponds to the atomistic region samples the
grand-canonial ensemble.  The question regarding the accuracy of
AdResS can be asked by: How accurately the atomistic region samples
the grand-canonial ensemble in the thermodynamic limit. Being more
specifically, we want to prove the probability density of the atomistic region satisfies
\begin{align}\label{eqn:dist-0}
  p(\vect x_\AT, N_\AT) \approx \frac{1}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT - \beta \mh^\AT(\vect x_\AT)} \Big\}
\end{align}
where $\mu^\ast_\AT$ is the chemical potential of reference system in
the desired equilibrium, $\mathcal Z$ is the partition function
normalizing the probability density, and $\mh^\AT$ is the \emph{atomistic}
Hamiltonian defined in the the subregion of the reference system that
corresponds to the atomistic region of the AdResS system.

@@

In the reference system (full atomistic), if the equilibrium state is achieved, then
the temperature, pressure and chemical potential of different regions are identical.
In AdResS system, the global uniform
temperture distrubution in equilibrium is equilibriated by the Langevin
thermostat.  However, extra term appear in the pressure or chemical
potential relations when the momentum or energy conservation is absent
(see Tab.~\ref{tab:conv-laws}), respectively.
